\section{Introduction}
This report covers our exam project for the mandatory \emph{Analysis, Design and Software Architecture}
course at our third semester at the BSc in Software Development at the IT-University of Copenhagen.
This project took place in November and December in the year 2012. 

Our advisors throughout this project have been Jacob Bardram and Dario Pacino. We have also received feedback from
our teacher's assistant, Simon Bang Terkildsen, who has been of great help to us.

\paragraph{The Problem}
The main purpose of this project is to document the making of a proof-of-concept of an interactive document
sharing-system, called Slice of Pie, which mixes some of the functionality of Google Drive and Dropbox with
an integrated text editor.
Concretely, the minimum requirements were:
\begin{itemize}
\item A document should include both text and images. The format of the document is up to you.
\item Documents can be arranged into folders or projects.
\item The history of changes on each document should be kept and be available to the users.
\item Local synchronization and off-line work mode should be implemented.
\item Documents can be shared and changes on the same document must be merged.
\end{itemize}
\paragraph{Our Slice}
Like Google Drive, Slice of Pie allows the user to create, edit, and share documents through a web interface.
Documents can be arranged into projects and folders. The modifications of shared documents are merged together.

It gives the user the possibility of having a local client and all files in a local version. A stand-alone client
application is provided which can perform the same operations as the web client. With the local client, the user
can also work offline.

Unlike Dropbox, Google Drive and the likes, our application is limited to simple text files.

The source code for the project may be found at\newline http://github.com/hypesystem/SliceOfPie/app.

\subsection{Our work}
As a group of five members, we have been dividing work between us for the most part. This is not, however, the case with the report itself, which has largely been a collaborative process.

\paragraph{SCRUM}
In our Scrum Team the role of Product Owner was assigned to Niels Roesen Abildgaard, while the role of ScrumMaster was assigned to Niclas Benjamin Tollstorff.

\paragraph{Code}
In the code part each member of the group have contributed to most parts, but each person has had specific focuses, which are listed here:\\

\begin{itemize}
\item Local Client: \textbf{Niclas Benjamin Tollstorff}
\item Web Client: \textbf{Jacob Stenum Czepluch}, \textbf{Sigurt Bladt Dinesen}, \textbf{Niels Roesen Abildgaard}
\item Local File Model: \textbf{Michael Mungkol Storgaard}
\item Web File Model: \textbf{Niels Roesen Abildgaard}
\item Controller: \textbf{Niels Roesen Abildgaard}
\item Merger: \textbf{Sigurt Bladt Dinesen}
\item Database (Entity Framework): \textbf{Michael Mungkol Storgaard}, \textbf{Sigurt Bladt Dinesen}
\end{itemize}
