\section{Vision}
\label{sec:vision}

The following is the vision for our product, almost exactly like it looked at its inception. Not much changed
over the course of three weeks.

\subsection{Positioning: Business Opportunity and Product Position Statement}
There already exists many cloud storage solutions and they offer a wide variety of specializations. We aim to create a simple, lightweight, and dedicated file-sharing application which also allows to editing documents.

Most existing solutions offer a wide range of features, but there are no simple and light clients out there.
Our product is aimed at people with simple text-editing needs.

\subsection{Stakeholder Description}
Users want to edit, create and delete files and have those actions synchronized automatically. They want to be able to share these files and allow multiple collaborators. The ability to work offline is also required by the users.

Use ranges from private to corporate, so stability is important.

\subsection{High-Level Goals}

\begin{itemize}
    \item High: Automatic Synchronization
    \item High: Offline Work 
    \begin{itemize}
        \item Concern: Full history merge on connection reestablished
        \item Concern: Timestamps out of sync
    \end{itemize}
    \item High: Merging of Concurrent Edits
    \begin{itemize}
        \item Concern: Corruption of data
    \end{itemize}
    \item Medium: Stability in Service
    \item Low: Identification
    \begin{itemize}
        \item Concern: Security flaws, false identities
    \end{itemize}
    \item Low: Encryption and Authentication
\end{itemize}
    
\subsection{User-Level Goals}

The following goals must be achievable local computers and external locations:
\begin{itemize}
    \item Create, delete and rename folders
    \item Share folders
    \item Change permissions of folder collaborators
    \item Create, edit and delete documents
    \item See a list of documents for each folder
    \item Review previous versions of a document
\end{itemize}

\subsection{User Environment}
The product is aimed at a wide variety of Windows computers as well as computers with modern browser capabilities.

\subsection{Summary of benefits}
We allow users to share files in an easy, interactive way with multiple users editing the same files, aiming to mitigate data corruption.

It becomes easy to share and collaborate on documents.